Austral Spring Extratropical Southern Hemisphere zonally assymetric circulation \thanks{The research was supported by UBACyT20020170100428BA and the CLIMAX Project funded by Belmont Forum/ANR-15-JCL/-0002-01. Elio Campitelli was supported by a PhD grant from CONICET, Argentina.}

### 2021-09-08 analysis/paper/shceof.tex
Render

@@

The influence of cEOFs variability in continental rainfall and 2-metre temperature in the Southern Hemisphere is also explored. Figure \ref{fig:pp-temp-2} show regression maps of 2-meter temperature (column 1) and precipitation (column 2) upon standardised cEOF2 which, again, can be interpreted as the anomalies associates with a 1 standard deviation increase.

>>>>

\begin{verbatim}
## Spherical geometry (s2) switched off
\end{verbatim}

@@

\begin{figure}
\centering
\includegraphics{../figures/pp-t2m-r2-1.pdf}
\caption{\label{fig:pp-t2m-r2}Explained variance (\(r^2\)) of 2-metre temperature (row a) and precipitation (row b) with cEOF1 (column 1) and cEOF2 (column 2).}
\end{figure}

The influence of cEOFs variability in continental rainfall and 2-metre temperature in the Southern Hemisphere is also explored.
Figure \ref{fig:pp-t2m-r2} shows the \(r^2\) between the cEOF1 and cEOF2 and 2-metre temperature and precipitation.
For the cEOF1 there are no significant signals in precipitation and most of the temperature signal is low and restricted to the eastern coast of Antarctica.

There is a strong signal between both variables and cEOF2, with explained variance greater than 50\% in some regions.
For 2-metre temperature, there are high values in the tropical Pacific and the SPCZ, as well as the region following an arc between New Zealand and the South Atlantic.
Over the continents, moderate values of about 30\% variance explained can be seen in southern Australia, some regions of South America and the Antarctic Peninsula.
For precipitation, there are high values over the tropics.
At higher latitudes, moderate values are observed over eastern Australia and some regions of southern South America.

Since the cEOF1 has a relatively weak signal, we will focus on the cEOF2.

Figure \ref{fig:pp-temp-2} shows regression maps of 2-meter temperature (column 1) and precipitation (column 2) upon standardised cEOF2 which, again, can be interpreted as the anomalies associates with a 1 standard deviation increase.
